\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-24 WOOT/Files/background.tex
add figures, add new counter measure
Figures

\section{Background}
\label{sec:background}
\shuqing{Maybe we could introduce HID devices somewhere.}
\noindent\outline{USB Standard}\\
We first introduce the development of USB specification and emphasize the key points adopted in our work. We also organized a brief timeline introducing key points of each protocol in Table~\ref{table:usb_timeline}.

\noindent\outline{USB1.x}\\
Proposed in 1996, USB 1.0\cite{usb10} was developed to provide an unified interface and thus reducing the cost of re-configuring the software. It is worth mentioning that as a polled-bus interface, all data transfers are initiated by the host.

\noindent\outline{HID Protocol}\\
Right after one year of the appearance of USB 1.0, a standard named HID (\emph{Human Interface Device})\hongyi{Citation Needed} was born on the basis of USB. HID is designed with the goal of unifying the implementation for devices like mouse, keyboard and so on. Before its appearance, the standard is divided between manufacturers, for example, mouses of Company A may uses X-Y coordinates to represent its location while mouses of Company B uses relative displacement. This means every device needs their own drivers to work. After HID, people just write one driver for an entire class of HIDs. Furthermore, HID standard also requires all devices to be PnP (\emph{Plug-and-Play}), which is indeed convenient but very dangerous too.

USB1.x\cite{usb10}\cite{usb11} provided two data transfer rates which are Low Speed (1.5 Mbit/s) and Full Speed (12 MBit/s). At this point, due to the transfer limit, it only supports limited kinds of devices like keyboard, mice, etc.

\noindent\outline{USB2.0}\\
In 2000, USB 2.0\cite{usb20} specification was released. With High Speed (480 Mbit/s) mode introduced, printer, camera, CD-ROM drive and network cards were supported in this revision. Such high data transfer rate also gave rise to the popularity of ``flash drive'', portable device that allows physically transferring data around \cite{sok}. Though various peripherals were supported in USB 2.0, there was no reliable way to identify the type of a device. This security flaw allowed attacks like BadUSB\cite{rubber}.

\noindent\outline{USB3.x}\\
USB 3.0\cite{usb30} was announced in 2008, with a Super Speed (5 Gbit/s) data transfer rate. Like its predecessor, more classes of peripherals were supported in this revision. In 2013, USB Type-C connector standard was introduced as a part of USB 3.1\cite{usb31}, providing a unified connector type for PowerDelivery (PD), Thunderbolt, DisplayPort and HDMI.  Yet no improvement of security was introduced in 3.x revisions, meaning any device claiming themselves as a monitor can capture the video stream from the host. Exposing such multi-propose connector unprotected is dangerous and allows attacks like our work \tool. In 2017, USB 3.2\cite{usb32} was released, doubling the data transfer rate. (20 Gbit/s)

\noindent\outline{Connector Standard}
\begin{figure}[hbtp]
	\includegraphics[width=\linewidth]{./Figs/usb_conn.png}
	\caption{USB 1.x \& 2.x Connector}
	\label{fig:usb_conn}
\end{figure}
As illustrated in Figure~\ref{fig:usb_conn}, the original USB 1.x \& 2.x connector only has two pins for data transferring (D+ \& D-), which has significantly limited data transfer rate (5 Gbits/s Max) and support for peripheral like DisplayPort (10.8 Gbit/s Min). Apart from that, support for other peripheral also requires dedicated transferring lane as their standards are not compatible with USB in most cases.
\begin{figure}[hbtp]
	\includegraphics[width=\linewidth]{./Figs/usb_c_conn.png}
	\caption{USB Type C Connector}
	\label{fig:usb_c_conn}
\end{figure}

@@

\noindent\outline{Security Problem}\\
During the development of USB specification, security was rarely considered.  As the USB-IF believes it is the duty of original equipment manufacturers (OEMs) to decide whether security features should be implemented.\hongyi{Citation needed}. But the divergent implementations give a chance for attack like BadUSB\cite{rubber} and our \tool.

>>>>

\section{Background}
\label{sec:background}
%\shuqing{Maybe we could introduce HID devices somewhere.}
%\noindent\outline{USB Standard}\\
We first introduce the development of USB specification and emphasize the key points adopted in our work. We also organized a brief timeline introducing key points of each protocol in Table~\ref{table:usb_timeline}.

%\noindent\outline{USB1.x}\\
Proposed in 1996, USB 1.0\cite{usb10} was developed to provide an unified interface and thus reducing the cost of re-configuring the software. It is worth mentioning that as a polled-bus interface, all data transfers are initiated by the host.

%\noindent\outline{HID Protocol}\\
Right after one year of the appearance of USB 1.0, a standard named HID (Human Interface Device)\hongyi{Citation Needed} was born on the basis of USB. HID is designed with the goal of unifying the implementation for devices like mouse, keyboard and so on. Before its appearance, the standard is divided between manufacturers, for example, mouses of Company A may uses X-Y coordinates to represent its location while mouses of Company B uses relative displacement. This means every device needs their own drivers to work. After HID, people just write one driver for an entire class of HIDs. Furthermore, HID standard also requires all devices to be PnP (\emph{Plug-and-Play}), which is indeed convenient but very dangerous too.

In 1998, the first widely supported USB protocol was born. USB1.1\cite{usb11} provided two data transfer rates which are Low Speed (1.5 Mbit/s) and Full Speed (12 MBit/s). At this point, due to the transfer limit, it only supports limited kinds of devices like keyboard, mice, etc.

%\noindent\outline{USB2.0}\\
In 2000, USB 2.0\cite{usb20} specification was released. With High Speed (480 Mbit/s) mode introduced, printer, camera, CD-ROM drive and network cards were supported in this revision. Such high data transfer rate also gave rise to the popularity of ``flash drive'', portable device that allows physically transferring data around \cite{sok}. Though various peripherals were supported in USB 2.0, there was no reliable way to identify the type of a device. This security flaw allowed attacks like BadUSB\cite{rubber}.

%\noindent\outline{USB3.x}\\
USB 3.0\cite{usb30} was announced in 2008, with a Super Speed (5 Gbit/s) data transfer rate. Like its predecessor, more classes of peripherals were supported in this revision. In 2013, USB Type-C connector standard was introduced as a part of USB 3.1\cite{usb31}, providing a unified connector type for PowerDelivery (PD), Thunderbolt, DisplayPort and HDMI.  Yet no improvement of security was introduced in 3.x revisions, meaning any device claiming themselves as a monitor can capture the video stream from the host. Exposing such multi-propose connector unprotected is dangerous and allows attacks like our work \tool. In 2017, USB 3.2\cite{usb32} was released, doubling the data transfer rate. (20 Gbit/s)

%\noindent\outline{Connector Standard}
\begin{figure}[t]
    \centering
	\includegraphics[width=0.7\linewidth]{./Figs/usb_conn.png}
	\caption{USB 1.x \& 2.x Connector}
	\label{fig:usb_conn}
\end{figure}
As illustrated in Figure~\ref{fig:usb_conn}, the original USB 1.x \& 2.x connector only has two pins for data transferring (D+ \& D-), which has significantly limited data transfer rate (5 Gbits/s Max) and support for peripheral like DisplayPort (10.8 Gbit/s Min). Apart from that, support for other peripheral also requires dedicated transferring lane as their standards are not compatible with USB in most cases.
\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{./Figs/usb_c_conn.png}
	\caption{USB Type C Connector}
	\label{fig:usb_c_conn}
\end{figure}

@@

%\noindent\outline{Security Problem}\\
During the development of USB specification, security was rarely considered.  As the USB-IF believes it is the duty of original equipment manufacturers (OEMs) to decide whether security features should be implemented.\hongyi{Citation needed}. But the divergent implementations give a chance for attack like BadUSB\cite{rubber} and our \tool.

### 2021-01-24 WOOT/Files/discussion.tex

\subsection{Limitation}
There exist multiple limitations of \tool.
To begin with, \tool can only gain the information and control access of the host itself instead of external hardware.
Consequently, as we introduced in the Section\ref{sec:countermeasures}, \tool can hardly bypass the defence approaches which use external hardware for authorization.
Moreover, most of the devices will prompt users to give authentication to the USB devices or select one of the functional modes after they are plugged in.
Though some of such prompts are not conspicuous for non-experts, especially when \tool is concealed within other functional hardware such as portable battery \shuqing{If there is experiment, add it here.}, the probability whether users could get aware that something unusual happens will increase with the existence these prompting messages.

>>>>

\subsection{Limitation}
There exist multiple limitations of \tool.
To begin with, \tool can only gain the information and control access of the host itself instead of external hardware.
Consequently, as we introduced in the Section\ref{sec:countermeasures}, \tool can hardly bypass the defence approaches which use external hardware for authorization.
Moreover, most of the devices will prompt users to give authentication to the USB devices or select one of the functional modes after they are plugged in.
Though some of such prompts are not conspicuous for non-experts, especially when \tool is concealed within other functional hardware such as power banks \shuqing{If there is experiment, add it here.}, the probability whether users could get aware that something unusual happens will increase with the existence these prompting messages.
